Sandbox BC Data

### 2020-11-15 scripts/draft_play.Rmd
added urban v. rural data
still a little messy

>>>>

```{r urban vs. rural}

bc_data_district_classification <- read_excel("C:/Users/makay/Dropbox (University of Oregon)/University of Oregon/Fall 2020/EDLD 651 Data Science/Final Project/bc_data_district_classification.xlsx")

district_class <- bc_data_district_classification %>%
  select("SCHOOL_YEAR",
         "DATA_LEVEL",
         "PUBLIC_OR_INDEPENDENT",
         "DISTRICT_NUMBER",
         "DISTRICT_NAME",
         "DISTRICT_POPULATION_2016",
         "DISTRICT_CLASSIFICATION",
         "SPECIAL_NEEDS_CODE",
         "NUMBER_OF_STUDENTS") %>%
  filter(DATA_LEVEL == "DISTRICT LEVEL",
         PUBLIC_OR_INDEPENDENT == "BC Public School")

```
